---
title: "TaxesVignette"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TaxesVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

Taxes is a simple package that allows users to input a state (or a vector of states) and it will return the given tax rate for those states. Append_tax_rates takes a data frame with a vector of states and adds another column to the data frame with the relevant tax rates.



This package also has a **budget** function that allows a user to input a state, a price of a good, and how much they are willing to pay. The function will calculate the tax rate for the price, and it will compare it to the budget.




$EXAMPLES$

`tax_rate("NC")`

return: 0.0698

`append_tax_rates(mydata$states, mydata)`

return:

  Tax Rate states 
1   6.25 %     MA   
2   5.75 %     VA 
3   8.52 %     NY 
4   6.98 %     NC   
5      6 %     MD 
6     NA %     OH 
7   7.01 %     FL 
8   7.35 %     GA 


`budget("MA", 300, 315)`

return: "Your tax-adjusted price is over your budget"












```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TaxesFinal)
```
