---
title: "Taxes"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{TaxesVignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---
#
Taxes is a simple package that allows users to input a state (or a vector of states) and it will return the given tax rate for those states. Append_tax_rates takes a data frame with a vector of states and adds another column to the data frame with the relevant tax rates.

##

This package also has a **budget** function that allows a user to input a state, a price of a good, and how much they are willing to pay. The function will calculate the tax rate for the price, and it will compare it to the budget.


###

**Function**: tax_rate(state)
    
{Argument}: state a string or vector containing states in the format "AB"
    
**Function**: append_tax_rates(data, data_frame)
    
{Argument}: data a vector containing states in the format "AB"
    
{Argument}: data_frame a data frame containing a vector of states
    
**Function** budget(state, price, budget)
    
{Argument}: price a numeric
    
{Argument} budget a numeric
     

$EXAMPLES$

####

`tax_rate("NC")`

return: 0.0698

`append_tax_rates(mydata$states, mydata)`

return:

| Tax Rate | States|
|---------:|:------|
|  6.25 %  |   MA  | 
|  5.75 %  |   VA  |
|  8.52 %  |   NY  | 
|  6.98 %  |   NC  |
|  6.00 %  |   MD  |



`budget("MA", 300, 315)`

return: "Your tax-adjusted price is over your budget"

#####










```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(TaxesFinal)
```
